Type Refinements for the Working Class

### 2015-11-20 paper.tex
Document renaming convention, stub appendix (#5)

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{leftidx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{catchfilebetweentags}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{ifdraft}
\usepackage{ifthen}
\usepackage{mathtools}
\usepackage{proof}
\usepackage{scalerel}
\usepackage{setspace}
\usepackage{stmaryrd}
\usepackage{supertabular}
\usepackage{tikz-cd}
\usepackage{tikzpfeile}
\usepackage{url}
\usepackage{todonotes}

@@

%% Recall from~\cite{sterling-morrison:2015} that
%% $\SCtx$ is the category of symbol-contexts and their injective, sort-preserving
%% renamings. Then, a \emph{judgment} shall be interpreted as an object in the presheaf
%% category $\Define{\mathbb{J}}{\Sets^\SCtx}$; in other words, a
%% judgment is identified with the intensional set of its renaming-sensitive
%% derivations. $\mathbb{J}$, like all presheaf categories, is a topos.

@@

\ifdraft{}{
  \nocite{maclane:1971}
  \bibliographystyle{abbrv}
  \bibliography{refs}
}

>>>>

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{leftidx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{catchfilebetweentags}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{ifdraft}
\usepackage{ifthen}
\usepackage{mathtools}
\usepackage{proof}
\usepackage{scalerel}
\usepackage{setspace}
\usepackage{stmaryrd}
\usepackage{supertabular}
\usepackage{tikz-cd}
\usepackage{tikzpfeile}
\usepackage{url}
\usepackage[titletoc,title]{appendix}
\usepackage{todonotes}

@@

\paragraph{Renaming convention} Because the evidence of a judgment will often
contain symbols $u,v,\dots$ we informally adopt the convention that the
evidence of a judgment shall always be subject to fresh renamings of its free
symbols (i.e.\ the validity of a judgment shall not depend on choice of names).
This apparatus is developed formally in Appendix~\ref{appendix:lf}, where the
logical framework is cast as a topos of covariant presheaves on symbol contexts
$\SCtx$.

%% Then, a \emph{judgment} shall be interpreted as an object in the presheaf
%% category $\Define{\mathbb{J}}{\Sets^\SCtx}$; in other words, a
%% judgment is identified with the intensional set of its renaming-sensitive
%% derivations. $\mathbb{J}$, like all presheaf categories, is a topos.

@@

\newpage
\begin{appendices}
\section{Formal Definition of the Logical Framework}
\label{appendix:lf}
\end{appendices}

\ifdraft{}{
  \newpage
  \nocite{maclane:1971}
  \bibliographystyle{abbrv}
  \bibliography{refs}
}
